Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/content/barriers.tex
edits

While combined these two advantages serve as strong barriers to entry a natural question to ask is would having only the data advantage or only the reputation advantage still serve as such strong barriers to entry? Which of the two serves as a stronger barrier to entry and under what conditions? In order to answer these questions we run two additional experiments, artificially modifying the previous temporary monopoly experiment. In one experiment the reputation of the incumbent is artificially erased upon the entry of the entrant (Reputation Erased Experiment) and in the other the information gained by the incumbent is artificially erased so that the posterior is reset to the prior (Information Erased Experiment).

@@

\begin{finding}
\textit{Maintaining either the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. \\ \indent When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $\DG$ there is no substantial difference between the two.}
\end{finding}

>>>>

While combined these two advantages serve as strong barriers to entry,
a natural question to ask is would having only the data advantage or
only the reputation advantage still serve as such strong barriers to
entry? Which of the two serves as a stronger barrier to entry and
under what conditions?

\swedit{To answer these questions, we isolate the effects from the two
  advantages and run two additional experiments. In the first
  experiment (called \emph{reputation erased experiment}), the
  reputation of the incumbent is artificially erased upon the entry of
  the entrant. In the second experiment (called \emph{information
    erased experiment}), the information gained by the incumbent is
  erased in the sense that its posterior is reset to the initial
  (fake) prior upon the entry of the entrant.}

\swcomment{Guy, could you make it clear what the first ``erase'' mean? Like reset to default?}

@@

\begin{finding}
\textit{Maintaining either the data or reputation advantage alone still allows the incumbent to retain a significant portion of the market. \swcomment{too vague. what does significant mean?}\\ \indent When the incumbent plays $\TS$, the data advantage serves as a larger barrier to entry compared to reputation, but when the incumbent plays $\DEG$ or $\DG$ there is no substantial difference between the two.}
\end{finding}
